### 2011-05-10 paper.tex
started oracle section
added remark

\newcommand{\bp}{\textsf{BP}}
\newcommand{\strongbp}{\textsf{strongBP}}
\newcommand{\parity}{\oplus}
\newcommand{\p}{\textsf{P}}
\newcommand{\op}{\textsf{Op}}

@@

\begin{theorem}\label{oracle}
Let $C$ be a class containing \emph{$\p$} which is closed under intersection. Then\linebreak \emph{$\parity \cdot (\p^{\parity \cdot C}) = \parity \cdot C$}.
\end{theorem}
\begin{proof}

\end{proof}

@@

@@

\bibitem{Toda2} Toda, S.; Ogiwara, M. \emph{Counting classes are at least as hard as the polynomial-time hierarchy,} Structure in Complexity Theory Conference, 1991, Proceedings of the Sixth Annual, pp. 2-12, 30 Jun-3 Jul 1991.

>>>>

\newcommand{\bp}{\textsf{BP}}
\newcommand{\strongbp}{\textsf{strongBP}}
\newcommand{\parity}{\oplus}
\newcommand{\p}{\textsf{P}}
\newcommand{\op}{\textsf{Op}}
\newcommand{\pp}{\textsf{PP}}

@@

\begin{theorem}\label{oracle}
Let $C$ be a class containing \emph{$\p$} which is closed under intersection. Then\linebreak \emph{$\parity \cdot (\p^{\parity \cdot C}) = \parity \cdot C$}.
\end{theorem}
\begin{proof}
The direction $\parity \cdot C \subseteq \parity \cdot (\p^{\parity \cdot C})$ is trivial. Let us consider the interesting direction\linebreak $\parity \cdot (\p^{\parity \cdot C})\subseteq \parity\cdot C$.
\end{proof}
\begin{remark}\emph{
While this paper applies Theorem \ref{oracle} only in the case where $C$ is $\{\Sigma,\Pi,\bp,\parity\}$-constructible, it can also be used to show, for instance, that $\parity \cdot (\p^{\parity \cdot \pp}) = \parity \cdot \pp$, although it is nontrivial to show that $\pp$ is closed under intersection. For a proof, see \cite{Beigel}.
}\end{remark}

@@

\bibitem{Beigel} Beigel, R., Reingold, N., and Spielman, D.A. \emph{PP is closed under intersection}, Proceedings of ACM Symposium on Theory of Computing 1991, pp. 1-9, 1991.

@@

\bibitem{Toda2} Toda, S. and Ogiwara, M. \emph{Counting classes are at least as hard as the polynomial-time hierarchy,} Structure in Complexity Theory Conference, 1991, Proceedings of the Sixth Annual, pp. 2-12, 30 Jun-3 Jul 1991.
